Tulai

### 2023-11-20 paper/paper.qmd
update the regional map

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[3],
           xmax = bbox[1],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           linewidth = 1.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = -0.02, # x location of inset placement
            y = -0.06, # y location of inset placement
            width = .6, # Inset width
            height = .4, # Inset height
            scale = 0.75 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))

>>>>

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[3],
           xmax = bbox[1],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           linewidth = 0.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = -0.02, # x location of inset placement
            y = 0.02, # y location of inset placement
            width = .6, # Inset width
            height = .4, # Inset height
            scale = 0.75 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))
